Presentation Title

### 2017-07-27 presentation/presentation.tex
Improve presentation

@@

% \subject{Theoretical Computer Science}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[] % Do nothing for \subsection*
{
  % do nothing
}

@@

\begin{frame}
  \titlepage
\end{frame}

@@

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\subsection{Motivation}
\begin{frame}{\subsecname}{}
  \begin{itemize}
    \item Blockchain systems offer an alternative to central authorities for the first time
    \item Market cap and trade volume figures indicate they are here to stay
    \item Early blockchain systems are not scalable (7 TX/s for Bitcoin)
    \item Parameter tuning leads to centralisation
  \end{itemize}
\end{frame}

\subsection{Research question}
\begin{frame}{\subsecname}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
\end{frame}

\subsection{Intuition}
\begin{frame}{\subsecname}{}
  \begin{itemize}
    \item A restaurant owner does not report all of its transactions with an central authority
    \item Ocassionally a customer may leave without paying and this event is reported to a central authority
    \item Our blockchain system achieves scalability using the same idea
  \end{itemize}
\end{frame}

\section{System architecture}
\subsection{System model}
\begin{frame}{\subsecname}
  \begin{itemize}
    \item Population size is $N$
    \item $n$ nodes are facilitators, $t$ nodes are malicious (Byzantine)
    \item $n \ge 3t + 1$
    \item $N \ge n + t$
    \item Purely asynchronous channels with eventual delivery
    \item Public key infrastructure
    \item Random oracle model
    \item Application neutural
  \end{itemize}
\end{frame}

\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture}
  \centering
  \end{figure}
\end{frame}

\subsection{Extended TrustChain}
\begin{frame}{\subsecname}
  \begin{itemize}
    \item Everyone has their own chain
    \item Two types of blocks, transaction (TX) blocks and checkpoint (CP) blocks
    \item A transaction involves two parties and results in two TX blocks
    \item A CP block captures the chain state
    \item TX and CP blocks are chained together using hash pointers
  \end{itemize}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-bad-cp}
  \centering
  \caption{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$.
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$.}
  \end{figure}
\end{frame}

\subsection{Consensus protocol}
\begin{frame}{\subsecname overview}
  \begin{enumerate}
    \item In round $r$, $n$ out of $N$ lucky nodes are selected at random to act as facilitators
    \item Facilitators run a BFT (Byzantine Fault Tolerant) consensus algorithm to
      agree on a set of CP blocks
    \item Disseminate the consensus result $\C_r$, i.e. the CP blocks
    \item Repeat
  \end{enumerate}
\end{frame}

\begin{frame}{\subsecname properties}
\label{def:consensus}
$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{itemize}
    \item \emph{Agreement}:
        If one correct node outputs a list of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ must hold for the $\C_r$ which was used to create $\F_r$,
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{itemize}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-1}
  \centering
  \caption{Suppose we are in a state where $\mathcal{C}_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result $\mathcal{C}_{r - 1}$,
    compute the new facilitators $\mathcal{F}_{r-1}$,
    and send out the new CP blocks.}
  \end{figure}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-4}
  \centering
  \caption{CP blocks at round $r-1$ should be in $\mathcal{C}_r$.
  The first $n$ nodes ordered by $\textsf{H}(\mathcal{C}_r || pk)$ become $\mathcal{F}_r$.}
  \end{figure}
\end{frame}

@@

\subsection{Validation protocol}
\begin{frame}{\subsecname overview}
\begin{itemize}
\item Request (\texttt{vd\_req}) and response (\texttt{vd\_resp}) protocol
\item Transactions are in three states---\emph{valid}, \emph{invalid} and \emph{unknown}
\item The goal is to identify which state a given transaction is in
\end{itemize}
\end{frame}

\begin{frame}{\subsecname properties}
\begin{itemize}
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Liveness}:
        Any valid transactions can be validated eventually.
\end{itemize}
\end{frame}

\begin{frame}{Validity definition}
\textbf{Function} $\textsf{get\_validity}()$ validates the transaction $t_{u, i}$
\vspace{5 mm}
\begin{algorithmic}
    \State Check that $v$ sent the correct agreed fragment,
    otherwise return \emph{unknown}.

    \State
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment TX exists

@@

@@

\subsection{Correctness of the consensus protocol}
\begin{frame}{\subsecname}
\begin{theorem}
For all rounds,
the consensus protocol satisfies agreement, validity, fairness and termination.
\end{theorem}
\begin{proof}(sketch)
Because consensus result are eventually delivered and the properties of ACS,
we get agreement, validity and termination.
Fairness is from the fact that we model $\textsf{H}(\cdot)$ as a random oracle (RO) and the input to the RO is different for every node,
thus the list of nodes ordered by $\textsf{H}(\C_r || pk )$ is a random permutation of those nodes.
\end{proof}
\end{frame}

\subsection{Correctness of the validation protocol}
\begin{frame}{\subsecname}
\begin{theorem}
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}(sketch)
Proof by contradiction.
For this attack to work, the adversary must be able to create two different fragments but with the same checkpoint enclosure.
We model $\textsf{H}(\cdot)$ as a RO, so the adversary need to query the RO a exponential\footnote{In terms of the security parameter.} number of times.
But the adversary can only query the RO a polynomial number of times.
\end{proof}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Prototype implementation on Github\footnote{\url{https://github.com/kc1212/consensus-thesis-code}}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Throughput vs population size (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\end{frame}

>>>>

\setbeameroption{show notes}

@@

\titlegraphic{\includegraphics[width=4cm]{logo}}

\AtBeginSubsection[] % Do nothing for \subsection*
{
  % do nothing
}

@@

\begin{frame}
  \titlepage

\end{frame}

@@

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\begin{frame}{Motivation}
  \begin{itemize}
    \item Blockchain systems offer an alternative to central authorities for the first time
    \item Market cap (40 billion for Bitcoin) and trade volume figures indicate they are here to stay
    \item Early blockchain systems are not scalable (7 TX/s for Bitcoin)
    \item Parameter tuning leads to centralisation
  \end{itemize}
\end{frame}

\begin{frame}{Research question}
    How do we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and can reach \emph{global consensus?}
    \note{
      \begin{itemize}
      \item Blockchain consensus protocol---independent of the application, like PoW (not PoS)
      \item Byzantine fault tolerance---if some number of nodes are malicious then the system should continue to function
      \item Horizontal scalability---if every node make transactions at the same rate, then the global throughput should increase
      \item Global consensus---all node should agree on a global state, useful for some applications, e.g. digital cash
      \end{itemize}
    }
\end{frame}

\begin{frame}{Inspiration}
  \begin{itemize}
    \item A restaurant owner does not report all of its transactions with an central authority
    \item Ocassionally a customer may leave without paying and this event is reported to a central authority
    \item Our blockchain system achieves scalability using a similar idea
  \end{itemize}
\end{frame}

\section{System architecture}
\subsection{System model}
\begin{frame}{\subsecname}
  \begin{itemize}
    \item Population size is $N$
    \item $n$ nodes are facilitators, $t$ nodes are malicious (Byzantine)
    \item $n \ge 3t + 1$
    \item $N \ge n + t$
    \item Purely asynchronous channels with eventual delivery
    \item Public key infrastructure
    \item Random oracle model
    \item Computational security
  \end{itemize}
  \note{At this point, explain facilitators are nodes that have some extra task to do, temporarily.}
\end{frame}

\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture}
  \centering
  \end{figure}
  \note{
    \begin{itemize}
    \item The primary data structure is the Extended TrustChain, extension of our prior work
    \item The three protocols the tasks as their name suggests
    \item They are independent and run concurrently
    \item The only synchronisation happens via the Extended TrustChain
    \item But in no part of those protocol do we lock the Extended TrustChain
    \end{itemize}
  }
\end{frame}

\subsection{Extended TrustChain}
\begin{frame}{\subsecname}
  \begin{itemize}
    \item Everyone has their own chain and genesis block
    \item Two types of blocks
      \begin{enumerate}
      \item Transaction (TX) block
      \item Checkpoint (CP) block
      \end{enumerate}
    \item A transaction involves two parties and results in two TX blocks (a pair)
    \item A CP block captures the chain state
    \item TX and CP blocks are chained together using hash pointers
  \end{itemize}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-good-cp}
  \centering
  \caption{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$.
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$.}
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

\begin{frame}{\subsecname:~fragment definition}
\begin{itemize}
\item A fragment $F_{u, i}$ is defined on a TX block $t_{u, i}$
\item It is a section of the chain beginning and ending with CP blocks that contains the TX
\end{itemize}
\end{frame}

\subsection{Consensus protocol}
\begin{frame}{\subsecname:~overview}
  \begin{enumerate}
    \item Runs in rounds
    \item In round $r$, $n$ out of $N$ act as facilitators
    \item The facilitators collect CP blocks from all nodes
    \item Facilitators run a Byzantine consensus algorithm to agree on a set of CP blocks
    \item Disseminate the consensus result $\C_r$, i.e. the CP blocks
    \item From $\C_r$, new facilitators are computed
    \item Repeat
  \end{enumerate}
\end{frame}

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{itemize}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ must hold for the $\C_r$ which was used to create $\F_r$,
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{itemize}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-1}
  \centering
  \caption{Suppose we are in a state where $\C_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result $\C_{r - 1}$,
    first $n$ nodes ordered by $\textsf{H}(\C_r || pk)$ become $\F_{r-1}$,
    send the new CP blocks to $\F_{r-1}$.}
  \end{figure}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-4}
  \centering
  \caption{$\F_{r-1}$ agree and disseminate $\C_r$,
  CP blocks at round $r-1$ ($c_{a, 6}, c_{b, 4}, c_{c,8}$) should be in $\C_r$.}
  \end{figure}
\end{frame}

@@

\subsection{Validation protocol}
\begin{frame}{\subsecname:~overview}
\begin{itemize}
\item Request (\texttt{vd\_req}) and response (\texttt{vd\_resp}) protocol
\item Transactions are in three states---\emph{valid}, \emph{invalid} and \emph{unknown}---defined by $\textsf{get\_validity}(\cdot)$
\item The goal is to identify which state a given transaction is in satisfying the validation protocol properties
\end{itemize}
\end{frame}

\begin{frame}{Validity definition}
\textbf{Function} $\textsf{get\_validity}(t_{u, i}, F)$ validates the transaction $t_{u, i}$
\vspace{5 mm}
\begin{algorithmic}
    \State Check that $v$ sent the correct $F$,
    otherwise return \emph{unknown}.

    \State
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment TX exists

@@

\begin{frame}{\subsecname:~properties}
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as validated (invalid) eventually.
\end{itemize}
\note{Liveness is not possible in our case because malicious nodes can simply go offline or refuse to respond,
but the other two properties are possible.}
\end{frame}

@@

\subsection{Correctness of the consensus protocol}
\begin{frame}{\subsecname}
\begin{theorem}
For all rounds,
the consensus protocol satisfies agreement, validity, fairness and termination.
\end{theorem}
\begin{proof}(sketch)
Because consensus result are eventually delivered and the properties of Byzantine consensus,
we get agreement, validity and termination.
Fairness is from the fact that we model $\textsf{H}(\cdot)$ as a random oracle (RO) and the input to the RO is different for every node,
thus the list of nodes ordered by $\textsf{H}(\C_r || pk )$ is a random permutation of those nodes.
\end{proof}
\end{frame}

\subsection{Correctness of the validation protocol}
\begin{frame}{\subsecname}
\begin{theorem}
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction according to the validity definition,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}(sketch)
Proof by contradiction.
For this attack to work, the adversary must be able to create two different fragments but with the same checkpoint enclosure.
We model $\textsf{H}(\cdot)$ as a RO, so the adversary need to query the RO a exponential\footnote{In terms of the security parameter.} number of times.
But the adversary can only query the RO a polynomial number of times.
\end{proof}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Prototype implementation on Github\footnote{\url{https://github.com/kc1212/consensus-thesis-code}}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
      \begin{itemize}
        \item Up to 30 machines
        \item Each running 40 nodes
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Throughput vs population size (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{neighbour-fixed/throughput-vs-population}
  \centering
  \end{figure}
\note{No need to request for fragment every time a TX needs to be validated. Upon receiving a fragment, validate as many TX as possible.}
\end{frame}

### 2017-07-27 thesis/chapters/ch3-model.tex
Update presentation
Improve presentation

If the enclosure of some TX block is $\langle c_{u,a}, c_{u, b} \rangle$,
then its \emph{fragment} is defined as $\{ b_{u, i} : a \le i \le b \}$.
For convenience, the function $\textsf{fragment}(\cdot)$ represents the fragment of some TX block if it exists, otherwise $\bot$.

@@

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a list of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ must hold for the $\C_r$ which was used to create $\F_r$,
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but they have some subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two asks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator list to the result.
This concludes the consensus phase and brings us back to the beginning of the consensus phase.

\begin{algorithm}
\caption{Function $\textsf{get\_facilitator}(C, n)$ takes a list of CP blocks $C$ and an integer $n$,
sort evey element in $C$ by its luck value (the $\lambda$-expression), and outputs the smallest $n$ elements.}
\label{alg:facilitator}
\begin{algorithmic}
\State $\textsf{take} (n, \textsf{sort\_by} (\lambda x.\textsf{H}(x || pk \text{ of } x), C))$
\end{algorithmic}
\end{algorithm}

@@

    \begin{algorithmic}
        \Upon $\langle \texttt{tx\_req}, t_{v, j} \rangle$ from $v$
        \State $txid, pk_v, m \gets t_{v, j}$ \Comment unpack the TX
        \State $\textsf{new\_tx}(pk_u, m, txid)$
        \State store $t_{v, j}$ as the pair of $t_{u, h}$
        \State send $\langle \texttt{tx\_resp}, t_{u, h} \rangle$ to $v$

        \Upon $\langle \texttt{tx\_resp}, t_{v, j} \rangle$ from $v$
        \State $txid, pk_v, m \gets t_{v, j}$ \Comment unpack the TX
        \State store $t_{v, j}$ as the pair of the TX with identifier $txid$
    \end{algorithmic}
\end{algorithm}

@@

    \State $c_{v, a} \gets \textsf{first}(F_{v, j})$
    \State $c_{v, b} \gets \textsf{last}(F_{v, j})$
    \If{$c_{v, a}$ or $c_{v, b}$ are not in consensus}
        \State \Return \emph{unknown}
    \EndIf \Comment $v$ has agreed fragment
    \State

@@

    % txid are equal now, but bad hash pointer
    \If{sequence number in $F_{v, j}$ is correct (sequential)}
        \If{hash pointers in $F_{v, j}$ is wrong}
            \State \Return \emph{unknown}
        \EndIf
    \EndIf \Comment correct TrustChain structure
    \State

    \State $c_{u, b} \gets \textsf{last}(F_{u, i})$
    \If{$c_{u, b}$ is not created using the same $\C_r$ as $c_{v, b}$}
        \State \Return \emph{unknown}
    \EndIf \Comment correct consensus round
    \State
    \label{line:valid-fragment}
    \State $txid, pk_v, m \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf \Comment TX exists
    \State

    \State $txid', pk'_u, m' \gets t_{v, j}$
    \If{$m \ne m' \vee pk_u \ne pk'_u$}
        \State \Return \emph{invalid}
    \EndIf \Comment no tampering
    \State

    \State \Return \emph{valid}
\end{algorithmic}
\end{algorithm}

@@

\begin{enumerate}
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid transactions can be validated eventually.
\end{enumerate}
\end{definition}

>>>>

If the enclosure of some TX block $t_{u, i}$ is $\langle c_{u,a}, c_{u, b} \rangle$,
then its \emph{fragment} $F_{u, i}$ is defined as $\{ b_{u, i} : a \le i \le b \}$.
For convenience, the function $\textsf{fragment}(\cdot)$ represents the fragment of some TX block if it exists, otherwise $\bot$.

@@

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ must hold for the $\C_r$ which was used to create $\F_r$,
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but they have some subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two asks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the beginning of the consensus phase.

\begin{algorithm}
\caption{Function $\textsf{get\_facilitator}(C, n)$ takes a set of CP blocks $C$ and an integer $n$,
sort evey element in $C$ by its luck value (the $\lambda$-expression), and outputs the smallest $n$ elements.}
\label{alg:facilitator}
\begin{algorithmic}
\State $\textsf{take} (n, \textsf{sort\_by} (\lambda x.\textsf{H}(x || pk \text{ of } x), C))$
\end{algorithmic}
\end{algorithm}

@@

    \begin{algorithmic}
        \Upon $\langle \texttt{tx\_req}, t_{v, j} \rangle$ from $v$
        \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{v, j}$
        \State $\textsf{new\_tx}(pk_u, m, txid)$
        \State store $t_{v, j}$ as the pair of $t_{u, h}$
        \State send $\langle \texttt{tx\_resp}, t_{u, h} \rangle$ to $v$

        \Upon $\langle \texttt{tx\_resp}, t_{v, j} \rangle$ from $v$
        \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{v, j}$
        \State store $t_{v, j}$ as the pair of the TX with identifier $txid$
    \end{algorithmic}
\end{algorithm}

@@

    \State $c_{v, a} \gets \textsf{first}(F_{v, j})$
    \State $c_{v, b} \gets \textsf{last}(F_{v, j})$
    \If{$c_{v, a}$ or $c_{v, b}$ are not in consensus}
        \State \Return \emph{unknown}
    \EndIf
    \State \Comment $v$ has agreed fragment

@@

    % txid are equal now, but bad hash pointer
    \If{sequence number in $F_{v, j}$ is correct (sequential)}
        \If{hash pointers in $F_{v, j}$ is wrong}
            \State \Return \emph{unknown}
        \EndIf
    \EndIf
    \State \Comment correct TrustChain structure

    \State $c_{u, b} \gets \textsf{last}(F_{u, i})$
    \If{$c_{u, b}$ is not created using the same $\C_r$ as $c_{v, b}$}
        \State \Return \emph{unknown}
    \EndIf
    \State \Comment correct consensus round
    \label{line:valid-fragment}
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment TX exists

    \State $\langle \_, \_, txid', pk'_u, m', \_ \rangle \gets t_{v, j}$
    \If{$m \ne m' \vee pk_u \ne pk'_u$}
        \State \Return \emph{invalid}
    \EndIf
    \State \Comment no tampering
    \State \Return \emph{valid}
\end{algorithmic}
\end{algorithm}

@@

\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transactions is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}
